### 2014-04-24 article.tex
Add in a new CC river regime figure.

    \end{tabular*}
    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two rivers. The calibration period was 01/01/1971 - 31/12/1975 and the validation period was 01/01/1976 - 31/12/1980.}
    \label{table:summary_stats}
\end{minipage} }
\end{table}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical2/river_cal}
    \caption{Simulated (blue line) plotted against observed (black crosses) for the two rivers.}
    \label{fig:river_cal}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical2/ctrl_river_regime}
    \caption{Simulated and observed river regimes calulcated over the combined calibration and validation periods.}
    \label{fig:ctrl_river_regime}
\end{figure}

@@

>>>>

    \end{tabular*}
    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two discharge stations. The calibration period was 01/01/1971 - 31/12/1975 and the validation period was 01/01/1976 - 31/12/1980.}
    \label{table:summary_stats}
\end{minipage} }
\end{table}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical2/river_cal}
    \caption{Simulated (blue line) plotted against observed (black crosses) for the discharge stations.}
    \label{fig:river_cal}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical2/ctrl_river_regime}
    \caption{Simulated and observed river regimes calculated over the combined calibration and validation periods.}
    \label{fig:ctrl_river_regime}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\textwidth]{geogg101_screenshots/practical2/effects_of_cc}
    \caption{River regimes showing the simulated effects of climate change under the Low, Medium and High emissions scenarios for both discharge monitoring stations. For reference, the simulated calibration/validation river regime is shown (black dashes). }
    \label{fig:effects_of_cc}
\end{figure}
